### 2019-01-03 taco/tex/evaluation.tex
Major revision

\begin{figure}
	\includegraphics[width=.8\linewidth]{fig/scache_util}
	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application with SCache}
	\label{fig:scache_util}
\end{figure}

@@

The second shuffle of Terasort partitions the data through a Spark RangePartitioner. 
% As the range bounds set by range partitioner almost match the same pattern of the first shuffle, almost $93\%$ of input data is from one particular map task for each reduce task. So we take the second shuffle as an extreme case to evaluate the scheduling locality for SCache.
In the second shuffle, almost $93\%$ of input data of a reduce task is produced by one particular map task. 
So we take the second shuffle as an extreme case to evaluate the heuristic locality swap of SCache.
In this shuffle, Spark schedules a reduce task to the node that produces most input data. 
By doing this, Spark minimizes the shuffle data through network. 
At the same time, Figure \ref{fig:terashuffle} reveals that SCache produces exactly same network traffic as Spark. 
It implies that the heuristic locality swap of SCache can obtain the best locality while balancing the load. 
\begin{figure}
	\centering
	\begin{subfigure}{.47\linewidth}
		\includegraphics[width=\linewidth]{fig/hadoop_terasort_scache}
		\caption{\color{blue}Hadoop MapReduce with SCache}
		\label{fig:hadoop_terasort_scache}
	\end{subfigure}
	\begin{subfigure}{.47\linewidth}
		\includegraphics[width=\linewidth]{fig/hadoop_terasort_origin}
		\caption{\color{blue}Hadoop MapReduce without SCache}
		\label{fig:hadoop_terasort_origin}
	\end{subfigure}
	\caption{\color{blue}CPU utilization and I/O throughput of a node during a Hadoop MapReduce Terasort job}
	\label{fig:hadoop_terasort}
\end{figure}
\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{fig/tpcds}
	\caption{TPC-DS Benchmark Evaluation}
	\label{fig:tpcds}
	\vspace{-1em}
\end{figure*}

@@

To prove SCache compatibility as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce as the external shuffle service and co-scheduler. Although \textit{pre-scheduling reduce tasks} is not critical for the simple DAG computing such as Hadoop MapReduce, some shuffle-heavy jobs on Hadoop MapReduce can still be optimized by SCache shuffle data management.

Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop MapReduce running Terasort. Both figures have the same proportion of time. Hadoop MapReduce with SCache brings $15\%$ of total time optimization with 384GB input data size. 
As shown in Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache writes intermediate data locally in the map phase. The shuffle phase and the reduce phase start simultaneously. Because a large amount of shuffle data reaches the network bottleneck, the beginning part of reduce needs to wait for network transfer. This causes the CPU resources to be idle. 
As shown in Figure \ref{fig:hadoop_terasort_scache}, Hadoop MapReduce with SCache starts pre-fetching in the map phase. This avoids the reduce phase waiting for the shuffle data. Furthermore, pre-fetching utilizes the idle I/O throughput in the map phase. As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop MapReduce with SCache optimizes Terasort overall completion time by up to $15\%$ and an average of $13\%$ with input data sizes from 128GB to 512GB.
}

>>>>

% \begin{figure}
% 	\includegraphics[width=.8\linewidth]{fig/scache_util}
% 	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application with SCache}
% 	\label{fig:scache_util}
% \end{figure}

@@

The second shuffle of Terasort partitions the data through a Spark RangePartitioner. 
% As the range bounds set by range partitioner almost match the same pattern of the first shuffle, almost $93\%$ of input data is from one particular map task for each reduce task. So we take the second shuffle as an extreme case to evaluate the scheduling locality for SCache.
In the second shuffle, almost $93\%$ of input data of a reduce task is produced by one particular map task. 
So we take the second shuffle as an extreme case to evaluate the heuristic locality swap of SCache.
In this shuffle, Spark schedules a reduce task to the node that produces most input data. 
By doing this, Spark minimizes the shuffle data through network. 
At the same time, Figure \ref{fig:terashuffle} reveals that SCache produces exactly same network traffic as Spark. 
It implies that the heuristic locality swap of SCache can obtain the best locality while balancing the load. 
\begin{figure}
	\centering
	\begin{subfigure}{.47\linewidth}
		\includegraphics[width=\linewidth]{fig/hadoop_terasort_scache}
		\caption{\color{blue}Hadoop MapReduce with SCache}
		\label{fig:hadoop_terasort_scache}
	\end{subfigure}
	\begin{subfigure}{.47\linewidth}
		\includegraphics[width=\linewidth]{fig/hadoop_terasort_origin}
		\caption{\color{blue}Hadoop MapReduce without SCache}
		\label{fig:hadoop_terasort_origin}
	\end{subfigure}
	\caption{\color{blue}CPU utilization and I/O throughput of a node during a Hadoop MapReduce Terasort job}
	\label{fig:hadoop_terasort}
\end{figure}
\begin{figure*}
	\centering
	\includegraphics[width=.9\textwidth]{fig/tpcds}
	\caption{TPC-DS Benchmark Evaluation}
	\label{fig:tpcds}
	\vspace{-1em}
\end{figure*}

@@

To prove SCache compatibility as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce. 
Although the effect of \textit{pre-scheduling} will be alleviated by the simple DAG computing, some shuffle-heavy jobs can still be optimized by SCache shuffle data management.

% Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop MapReduce running Terasort. Both figures have the same proportion of time. 
As Figure \ref{fig:hadoop_terasort} shows, Hadoop MapReduce with SCache brings $15\%$ of total time optimization with 384GB input data size. 
As shown in Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache writes intermediate data locally in the map phase. The shuffle phase and the reduce phase start simultaneously. Because a large amount of shuffle data reaches the network bottleneck, the beginning part of reduce needs to wait for network transfer. This causes the CPU resources to be idle. 
On the other hand, in Figure \ref{fig:hadoop_terasort_scache}, Hadoop MapReduce with SCache starts pre-fetching in the map phase. This avoids the reduce phase waiting for the shuffle data. Furthermore, pre-fetching utilizes the idle I/O throughput in the map phase. As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop MapReduce with SCache optimizes Terasort overall completion time by up to $15\%$ and an average of $13\%$ with input data sizes from 128GB to 512GB.
}

### 2019-01-03 taco/tex/impl.tex
Major revision

% {\color{red}
% \subsection{Cost of adapting DAG frameworks}
% SCache provides API through RPC, such as \textit{putBlock(blockId)}, \textit{getBlock(blockId)}, and \textit{getScheduleResult(shuffleId)}. The concise design makes it easy to adapt DAG frameworks to enable SCache optimization. For example, it only takes about 500 lines of code in Spark to integrate SCache. By a glance of Hadoop source code, we believe that the costs of enabling SCache on MapReduce \cite{hadoop} and YARN \cite{yarn} based DAG computing framework, such as Tez \cite{tez}, are also very low.
% }
{\color{blue}
\subsection{Analysis of cross-framework capability}\label{crossframework}
Shuffle optimization of SCache inevitably requires the modification on DAG frameworks. SCache provides APIs through RPC, such as \textit{putBlock (blockId)}, \textit{getBlock (blockId)}, and \textit{getScheduleResult (shuffleId)}. In order to use SCache, we mainly need to modify two parts of the frameworks: (a) We need to modify codes in the DAG scheduler to let framework provide DAG information and follow the pre-scheduled result of SCache; (b) The shuffle data between the map task and the reduce task should be transferred to SCache Storage Management.

To prove the cross-framework capability of SCache, we adapt SCache on Hadoop MapReduce and Spark respectively. Taking Hadoop MapReduce as an example, we modify codes in ResourceManager, MapTask, and ReduceTask to call SCache APIs through RPC. It takes about 400 lines of code. In Spark, we mainly modify DAGScheduler and the corresponding data fetcher. 
It only takes about 500 lines of code. Such hundreds of lines of code modification are very small compared to the hundreds of thousands of lines of code in DAG framework. We believe that the costs of enabling SCache on other DAG computing frameworks, such as Tez \cite{tez}, are also very low.
}

>>>>

% {\color{red}
% \subsection{Cost of adapting DAG frameworks}
% SCache provides API through RPC, such as \textit{putBlock(blockId)}, \textit{getBlock(blockId)}, and \textit{getScheduleResult(shuffleId)}. The concise design makes it easy to adapt DAG frameworks to enable SCache optimization. For example, it only takes about 500 lines of code in Spark to integrate SCache. By a glance of Hadoop source code, we believe that the costs of enabling SCache on MapReduce \cite{hadoop} and YARN \cite{yarn} based DAG computing framework, such as Tez \cite{tez}, are also very low.
% }
{\color{blue}
\subsection{Analysis of cross-framework capability}\label{crossframework}
Shuffle optimization of SCache inevitably requires the modification on DAG frameworks. SCache provides APIs through RPC, such as \textit{putBlock (blockId)}, \textit{getBlock (blockId)}, and \textit{getScheduleResult (shuffleId)}. In order to use SCache, we mainly need to modify two parts of the frameworks: (a) The DAG scheduler should provide the DAG information and follow the pre-scheduled result of SCache; (b) The shuffle data should be transferred to SCache Storage Management.

To prove the cross-framework capability of SCache, we adapt SCache on Hadoop MapReduce and Spark respectively. In Hadoop MapReduce, we modify codes in ResourceManager, MapTask, and ReduceTask to call SCache APIs through RPC. It takes about 380 lines of code. In Spark, we mainly modify DAGScheduler and the corresponding data fetcher. 
It only takes about 500 lines of code. Such hundreds of lines of code modification are very small compared to the hundreds of thousands of lines of code in DAG framework. We believe that the costs of enabling SCache on other DAG computing frameworks, such as Tez \cite{tez}, are also very low.
}

### 2019-01-03 taco/tex/intro.tex
Major revision

@@

{\color{yellow}
Various efforts of performance optimization have been made among computing frameworks, both at the software and hardware levels \cite{sync, tachyon, heintz2016end, zhang2015prism, cheng2017improving, chen2017heterogeneous}. However, the shuffle phase is often poorly optimized in practice.
% }
% {\color{red}
% Although continuous efforts of performance optimization have been made among a variety of computing frameworks\cite{sync, babu, tachyon, pacman, quincy, delay, ibrahim2012maestro, sharma2012mrorchestrator}, 
% the shuffle is often poorly optimized in practice.
% }
% take over shuffle
%shuffle characteristic
In particular, we observe that one major deficiency lies in the lack of fine-grained, coordinated management among different system resources.
%In the current practice, the shuffle phase is often split into two parts --- \textit{shuffle read} and \textit{shuffle write}. 
As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stages (i.e., map task).  
And the \textit{shuffle read} fetches intermediate results from remote disks through network, which is commonly integrated as part of the tasks in descendant stages (i.e., reduce task). 
Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk, and network) named \textit{slot} is assigned to a task, and the resources are released only after the task finishes.
Such task aggregation together with the coarse-grained scheduling effectively simplifies task management.
However, since a cluster has a limited number of slots, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
%The map task in Figure \ref{fig:workflow} well explains such deficiency: the I/O resource allocated to the stage is always idle during the computation time, and the computation/memory resource is totally wasted during the shuffle write attached to it, and vice versa.
\begin{figure}
	\centering
	\includegraphics
		[width=.6\linewidth]
		{fig/workflow}
	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
	\label{fig:workflow}
\end{figure}

@@

{\color{blue}
In order to analyze above-mentioned resources scheduling strategies, we propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model. The FRQ model quantifies computing and I/O resources and visualizes the resources scheduling strategies of DAG frameworks in the time dimension. We use the FRQ model to assist in analyzing the deficiencies of resources scheduling and optimize it. 
The FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
According to the above five parameters and the scheduling strategy of the DAG framework, the FRQ model is able to predict the execution time of each phase of a computing job. 
Taking Apache Hadoop MapReduce as a simple DAG computing example, we model each phase of the computing by the FRQ model, including Map, Shuffle, and Reduce.
By revealing the relationships between the various phases, the FRQ model assists us in discovering the irrationality of resource scheduling during computing.
I/O resources in the map phase are not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
This situation will be amplified in shuffle-heavy tasks.
}

>>>>

\begin{figure}
	\centering
	\includegraphics
		[width=.5\linewidth]
		{fig/workflow}
	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
	\label{fig:workflow}
\end{figure}

@@

{\color{blue}
Various efforts of performance optimization have been made among computing frameworks, both at the software and hardware levels \cite{sync, tachyon, heintz2016end, zhang2015prism, cheng2017improving, chen2017heterogeneous, yviquel2018cluster, kaitoua2014hadoop, wasi2017comprehensive}. However, the shuffle phase is often poorly optimized in practice.
}
% {\color{red}
% Although continuous efforts of performance optimization have been made among a variety of computing frameworks\cite{sync, babu, tachyon, pacman, quincy, delay, ibrahim2012maestro, sharma2012mrorchestrator}, 
% the shuffle is often poorly optimized in practice.
% }
% take over shuffle
%shuffle characteristic
In particular, we observe that one major deficiency lies in the lack of fine-grained, coordinated management among different system resources.
%In the current practice, the shuffle phase is often split into two parts --- \textit{shuffle read} and \textit{shuffle write}. 
As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stages (i.e., map task).  
And the \textit{shuffle read} fetches intermediate results from remote disks through network, which is commonly integrated as part of the tasks in descendant stages (i.e., reduce task). 
Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk, and network) named \textit{slot} is assigned to a task, and the resources are released only after the task finishes.
Such task aggregation together with the coarse-grained scheduling effectively simplifies task management.
However, since a cluster has a limited number of slots, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
%The map task in Figure \ref{fig:workflow} well explains such deficiency: the I/O resource allocated to the stage is always idle during the computation time, and the computation/memory resource is totally wasted during the shuffle write attached to it, and vice versa.

@@

{\color{blue}
In order to analyze above-mentioned resources scheduling strategies, we propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model. The FRQ model quantifies computing and I/O resources and visualizes the resources scheduling strategies of DAG frameworks in the time dimension. We use the FRQ model to assist in analyzing the deficiencies of resources scheduling and optimize it. 
The FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
According to the above five parameters and the scheduling strategy of the DAG framework, the FRQ model is able to predict the execution time of each phase of a computing job. 
Taking Apache Hadoop MapReduce as a simple DAG computing example, we model each phase of the computing by the FRQ model, including Map, Shuffle, and Reduce.
By revealing the relationships between the various phases, the FRQ model assists us in discovering the irrationality of resource scheduling during computing.
% I/O resources in the map phase are not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
% This situation will be amplified in shuffle-heavy tasks.
}
